---
title: "Shiny Application Presentation"
subtitle: "S&P 500 Stock Analysis"
author: "Horace Cheng"
widgets: [mathjax]
output: slidy_presentation
---

## Shiny Application: S&P 500 Stock Analysis

- Get Stock Price from [Yahoo Finance](http://finance.yahoo.com/)
- Can choose date range
- Support 3 types of data range: *daily*, *weekly*, *monthly*
- Hide/Show Volume data
- Implement 4 common technical analysis index: 
    + **Simple Moving Average**
    + **Weighted Moving Average**
    + **Exponential Moving Average** 
    + **Bollinger Bands**
- Integrate with *[Highcharts](http://www.highcharts.com/)*: a popular open source charting library for financial data
- Display calaulation results on Chart

## Why Use HighCharts
- Good support in **OHLC Chart**
- Integrate with rChart
- Based on the work of [Highstock-rCharts-hack](https://github.com/nemonominem/Highstock-rCharts-hack)
- Some enhancement:
    * Refactor 2 functions(ohlcvPlot and ohlcPlot) into 1 function(ohlcPlot)
    * Support add line on OHLC Chart

## Technical Analysis(Moving Average I)
- **Simple Moving Average** and **Weighted Moving Average**: Reference [Moving average](http://en.wikipedia.org/wiki/Moving_average)
$$SMA(n)_{M} = \frac{P_{M} + P_{M-1} + ... + P_{M-(n-1)}}{n}$$
$$WMA(n)_{M} = \frac{nP_{M} + (n-1))P_{M-1} + ... + 2P_{M-(n-2)} + P_{M-(n-1)}}{n + (n-1) + ... + 2 + 1)}$$
```{r}
MA <- function(data, step = 20, type = "sma", alpha = 0) {
  w <- sapply(1:step, function(x) {
    if (type == "wma") {
      step - x + 1
    } else {
      1
    }
  })
  ma <- data.frame(matrix(NA, nrow = dim(data)[1]-step+1, ncol = 2))
  colnames(ma) <- c("date", "Close")
  ma$date <- data[step:dim(data)[1],c("date")]
  ma$Close <- apply(data[step:dim(data)[1],], 1, function(x) {
    idx <- which(data$Date == x["Date"])
    start <- idx-step+1    
    round(sum(data[start:idx, c("Close")] * w)/sum(w) , 2)
  })
  ma
} 
```

## Technical Analysis(Moving Average II)
- **Exponential Moving Average**: Reference [Moving average](http://en.wikipedia.org/wiki/Moving_average)
$$EMA_{today} = \alpha * P_{today} + (1-\alpha)*EMA_{yesterday}, \alpha = 2/(n+1)$$
```{r}
EMA <- function(data, alpha = 1) {
  rows <- dim(data)[1]
  ema <- data.frame(matrix(NA, nrow = rows, ncol = 2))
  colnames(ema) <- c("date", "Close")
  ema$date <- data[,c("date")]
  for (i in 1:rows) {
    price <- data$Close[i]
    if (i == 1) {
      ema[i, c("Close")] <- price
    } else {
      ema[i, c("Close")] <- alpha * price + (1 - alpha) * ema$Close[i-1]
    }
  }
  ema
}
```

## Technical Analysis(Bollinger Bands)
- Reference [Bollinger Bands](http://en.wikipedia.org/wiki/Bollinger_Bands)
```{r}
BollingerBand <- function(data, step = 20, std = 2) {
  rows <- dim(data)[1]
  bol <- data.frame(matrix(NA, nrow = rows - step+1, ncol = 4))
  colnames(bol) <- c("date", "upper", "lower", "ma")
  bol$date <- data[step:rows,c("date")]
  bol[,c("upper","lower", "ma")] <- t(sapply(1:(rows-step+1), function(x) {
     end <- x + step - 1
     sd_roll <- sd(data[x:end, c("Close")])
     ma_roll <- mean(data[x:end, c("Close")])
     c(round(ma_roll + std*sd_roll, 2), 
       round(ma_roll - std*sd_roll, 2), 
       round(ma_roll, 2))
   }))
  bol
}
```